Regression Discontinuity Design to Measure Incumbency Advantage in U.S. Congressional Elections

### 2023-04-25 paper.qmd
give up on cross ref

First, we test the continuity of the Democratic vote margin for all $t-1$ elections in our data set. The results of the McCrary density test on the Democratic vote margin at the zero margin cutoff indicates a continuous density on both sides of the cutoff value ($\alpha = 0.05$). A plot of the McCrary density test’s density estimation is provided in @density-all.

```{r}
#| fig-cap: McCrary density test and estimation for all $t-1$ Democratic vote margins.
#| label: density-all

@@

With these three pretreatment covariates chosen, we estimate the discontinuities in their conditional densities conditional on the $t-1$ Democratic election margin at the zero margin value using local linear regression and find that there are no statistically significant discontinuities in either three covariates’ densities. This result can also be expected just by visual inspection of the covariate value versus the $t-1$ Democratic election margin, as in @covars.

```{r}
#| fig-cap: Three pretreatment covariates versus $t-1$ Democratic vote margin.
#| label: covars

@@

```{r}
#| label: basic-rdd
#| fig-cap: RDD analysis of 4,800 elections from 1976 through 2020. The local average treatment effect is 0.173.

@@

We found a clear discontinuity from a slight Democratic loss to a slight Democratic victory. A district that votes barely against the Democrat in election $t-1$ tends to shift further away from Democrats in election $t$, while districts that only marginally elect a Democrat in election $t-1$ move toward Democrats in election $t$. This is a clear effect of the treatment — in this case, electing a Democrat — on the Democratic margin in the next election. See @basic-rdd.

>>>>

First, we test the continuity of the Democratic vote margin for all $t-1$ elections in our data set. The results of the McCrary density test on the Democratic vote margin at the zero margin cutoff indicates a continuous density on both sides of the cutoff value ($\alpha = 0.05$). A plot of the McCrary density test’s density estimation is provided below.

```{r}
#| fig-cap: McCrary density test and estimation for all $t-1$ Democratic vote margins.

@@

With these three pretreatment covariates chosen, we estimate the discontinuities in their conditional densities conditional on the $t-1$ Democratic election margin at the zero margin value using local linear regression and find that there are no statistically significant discontinuities in either three covariates’ densities. This result can also be expected just by visual inspection of the covariate value versus the $t-1$ Democratic election margin.

```{r}
#| fig-cap: Three pretreatment covariates versus $t-1$ Democratic vote margin.

@@

We found a clear discontinuity from a slight Democratic loss to a slight Democratic victory. A district that votes barely against the Democrat in election $t-1$ tends to shift further away from Democrats in election $t$, while districts that only marginally elect a Democrat in election $t-1$ move toward Democrats in election $t$. This is a clear effect of the treatment — in this case, electing a Democrat — on the Democratic margin in the next election.

```{r}
#| fig-cap: RDD analysis of 4,800 elections from 1976 through 2020. The local average treatment effect is 0.173.

@@
